The interactions of rational, pragmatic agents\\ lead to efficient language structure and use

### 2019-02-01 paper/paper.Rmd
fix typo, almost good to go

How do the competing pressures of speakers and listeners give rise to the distributional regularities found in natural language? Zipf [-@Zipf1949a] proposed that the asymmetry between speaker and listener costs gives rise to a range of properties at the level of the lexicon. We explored the interactions of rational pragmatic agents as a framework for understanding efficient language structure and use. We focused on an argument on the communicative function of ambiguity [@Piantadosi2011a], deriving a novel speaker-listener Cross-Entropy objective for measuring the efficiency linguistic systems from first principles of efficient language use. In a series of simulations we showed that optimal languages are more likely to contain ambiguous material when context is informative and that rational pragmatic agents will use ambiguous material efficiently.\par

>>>>

How do the competing pressures of speakers and listeners give rise to the distributional regularities found in natural language? Zipf [-@Zipf1949a] proposed that the asymmetry between speaker and listener costs gives rise to a range of properties at the level of the lexicon. We explored the interactions of rational pragmatic agents as a framework for understanding efficient language structure and use. We focused on an argument on the communicative function of ambiguity [@Piantadosi2011a], deriving a novel speaker-listener Cross-Entropy objective for measuring the efficiency of linguistic systems from first principles of efficient language use. In a series of simulations we showed that optimal languages are more likely to contain ambiguous material when context is informative and that rational pragmatic agents will use ambiguous material efficiently.\par

### 2019-02-01 paper/paper.tex
fix typo, almost good to go

How do the competing pressures of speakers and listeners give rise to
the distributional regularities found in natural language? Zipf (1949)
proposed that the asymmetry between speaker and listener costs gives
rise to a range of properties at the level of the lexicon. We explored
the interactions of rational pragmatic agents as a framework for
understanding efficient language structure and use. We focused on an
argument on the communicative function of ambiguity (Piantadosi et al.,
2011), deriving a novel speaker-listener Cross-Entropy objective for
measuring the efficiency linguistic systems from first principles of
efficient language use. In a series of simulations we showed that
optimal languages are more likely to contain ambiguous material when
context is informative and that rational pragmatic agents will use
ambiguous material efficiently.\par

>>>>

How do the competing pressures of speakers and listeners give rise to
the distributional regularities found in natural language? Zipf (1949)
proposed that the asymmetry between speaker and listener costs gives
rise to a range of properties at the level of the lexicon. We explored
the interactions of rational pragmatic agents as a framework for
understanding efficient language structure and use. We focused on an
argument on the communicative function of ambiguity (Piantadosi et al.,
2011), deriving a novel speaker-listener Cross-Entropy objective for
measuring the efficiency of linguistic systems from first principles of
efficient language use. In a series of simulations we showed that
optimal languages are more likely to contain ambiguous material when
context is informative and that rational pragmatic agents will use
ambiguous material efficiently.\par
